\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2017-11-23 document/XSGRB_sample.tex
Remove bad nhx

In this section we describe the efficiency of the follow-up effort and the
characteristics of the observed bursts. We also assess the degree to which the
sample obtained is complete. An important note is that here we present
\textit{all} GRBs that have ever been observed with X-shooter, while only a
subset of these constitute our \textit{statistical} sample. The statistical
sample is based on the selection criteria described in Sect. \ref{samplecrit}
and should represent an unbiased sample of the underlying, parent GRB
population. Single bursts outside the sample criteria have been followed up on
the basis of the curiosity of their light curve or their brightness, but is not
discussed as part of the investigation of the GRB population. A prime example of
a burst outside the statistical sample is GRB161023A with it's rich
spectrum containing 11 intervening absorption systems and pending further analysis.

>>>>

In this section we describe the efficiency of the follow-up effort and the
characteristics of the observed bursts. We also assess the degree to which the
sample obtained is complete. An important note is that here we present
\textit{all} GRBs that have ever been observed with X-shooter, while only a
subset of these constitute our \textit{statistical} sample. The statistical
sample is based on the selection criteria described in Sect. \ref{samplecrit}
and should represent an unbiased sample of the underlying, parent GRB
population. Single bursts outside the sample criteria have been followed up on
the basis of the curiosity of their light curve or their brightness, but is not
discussed as part of the investigation of the GRB population. A prime example of
a burst outside the statistical sample is GRB~161023A with it's rich
spectrum containing 11 intervening absorption systems and pending further analysis.
